% ACKNOWLEDMENT FILE
\chapter*{Acknowledgments}
\markboth{Acknowledgments}{Acknowledgments}
\setstretch{1.4}
\normalsize
I would like to express my deepest gratitude to my thesis supervisor, Giovanni Simonini, for his invaluable guidance and support throughout the course of my research. His expertise and insightful feedback not only helped shape this thesis but also introduced me to fascinating fields in AI and Data Science. While this research was undoubtedly challenging, his mentorship made it an enriching and enjoyable journey.

I am profoundly and immeasurably grateful to my mother, father, and dear brother for their unwavering support and encouragement throughout my academic career. Their endless sacrifices, unconditional love, and steadfast belief in me have been my greatest source of strength. In times of doubt and difficulty, their guidance and reassurance lifted me up, providing me with the courage to keep pushing forward. Words cannot truly capture how deeply I appreciate their presence in my life, for they have been my foundation, my motivation, and my greatest blessing.

A heartfelt thank you to my friends who embarked on this academic journey alongside me: Arman Arnautović, Daniele Manicardi, Gianluca Mancusi, Vipul Kumar, and Marco Mezzina. The shared struggles, insights, and collaborative efforts were invaluable throughout my undergraduate years. I wouldn’t have been able to access the Master’s program without them, and for that, I am deeply grateful. I cherish our friendship and the many precious moments we have shared together.

To my incredible group of friends—Samuele Carretti, Loredana Hasani, Valeria Iacomini, Matteo Caccetta, and Francesco Tahiri—thank you for providing a community filled with shared passions and a drive for self-expression. Your companionship has been a source of emotional support, especially in the hardest of times, and I am deeply appreciative of the bond we share. Beyond that, the joy we have found in our shared passions and the unforgettable experiences we have created together have been truly invaluable. I am grateful for each and every moment we have spent together.

A profound thank you to all my friends who have been a welcoming presence in my life, making every shared moment a joy to experience: Adela Arnautović, Davide Federzoni, Lorenzo Solmi, Marian Dediu, Roberto Terrasi, Alessio Zella, Matteo Vanzini, Marco Difonzo, Matteo Ballotta, Ionut Sanduc, Sara Morandi, Axl Nava, and Manuel Caminiti. Your friendship has enriched my life in countless ways.

A heartfelt thank you to my colleagues and friends at the UNIMORE Department of Engineering Enzo Ferrari for their assistance and the pleasure of working alongside them. Their talents and dedication inspired me to push myself further, shaping both my academic and professional work ethic. Their camaraderie, discussions, and shared experiences have made this journey more rewarding and formative. I would like to express my gratitude to Sara Pederzoli, Vincenzo Macellaro, Sara Ferrari, Diego Mercoliano, Emiliano Maccaferri, Giacomo Salici, Angelo Mozzillo, Paolo Attardi, Michele Giarletta, Davide Palma, Vincenzo Lapadula, Riccardo Santi, Andrea Agguzzoli, Marco Savarese, Carmenia Basile, Francesca Palazzo, Giovanni Malaguti, Biagio Grimolizzi, Stefano Politanó, Marco Pirrelli, Antonio Solida, Elisa Tomisani, Luca Catalano, Valeria Coloca, Manuel Valbusa, Carmine Zaccagnino, Michele Mosca, Giuseppe Orefice, Aslam Kalam, Marco Francesco Sette, Felice Schena, Adeel Aslam, Luca Corrado, Antonio De Blasi, and Gianmarco Lusvardi.

To those who are no longer part of my life, I want to express my heartfelt gratitude for the role you played in shaping me into the person I am today. I cherish the good moments we shared, even the smallest ones, despite any challenges that arose along the way. Every experience, lesson, and connection—both uplifting and difficult—has contributed to my growth, and I would not change a thing from the past, as every step has led me to this moment. Wherever life takes you, I offer my sincere and authentic support for your struggles and future endeavors. I am proud of you and truly wish you happiness and success in all that you pursue.

Lastly, I extend my appreciation to all those who have contributed to this work, directly or indirectly. Your support, encouragement, and presence have been invaluable, and for that, I offer my heartfelt thanks.

