% ACKNOWLEDMENT FILE
\chapter*{Acknowledgments}
\markboth{Acknowledgments}{Acknowledgments}
\setstretch{1.5}
\normalsize
I would like to express my deepest gratitude to my thesis supervisor, Giovanni Simonini, for his invaluable guidance and support throughout the course of my research. His expertise and insightful feedback not only helped shape this thesis but also introduced me to fascinating fields in AI and Data Science. While this research was undoubtedly challenging, his mentorship made it an enriching and enjoyable journey.

I am profoundly and immeasurably grateful to my mother, father, and dear brother for their unwavering support and encouragement throughout my academic career. Their endless sacrifices, unconditional love, and steadfast belief in me have been my greatest source of strength. In times of doubt and difficulty, their guidance and reassurance lifted me up, providing me with the courage to keep pushing forward. Words cannot truly capture how deeply I appreciate their presence in my life, for they have been my foundation, my motivation, and my greatest blessing.

A heartfelt thank you to my friends who embarked on this academic journey alongside me: Arman Arnautović, Daniele Manicardi, Gianluca Mancusi, Vipul Kumar, and Marco Mezzina. The shared struggles, insights, and collaborative efforts were invaluable throughout my undergraduate years. I wouldn’t have been able to access the Master’s program without them, and for that, I am deeply grateful. I cherish our friendship and the many precious moments we have shared together.

To my incredible group of friends—Samuele Carretti, Loredana Hasani, Valeria Iacomini, Matteo Caccetta, and Francesco Tahiri—thank you for providing a community filled with shared passions and a drive for self-expression. Your companionship has been a source of emotional support, especially in the hardest of times, and I am deeply appreciative of the bond we share. Beyond that, the joy we have found in our shared passions and the unforgettable experiences we have created together have been truly invaluable. I am grateful for each and every moment we have spent together.

A profound thank you to all my friends who have been a welcoming presence in my life, making every shared moment a joy to experience: Adela Arnautović, Davide Federzoni, Lorenzo Solmi, Marian Dediu, Roberto Terrasi, Alessio Zella, Matteo Vanzini, Marco Difonzo, Matteo Ballotta, Ionut Sanduc, Sara Morandi, Axl Nava, and Manuel Caminiti. Your friendship has enriched my life in countless ways.

I extend my deepest gratitude to my colleagues and friends at the UNIMORE Department of Engineering Enzo Ferrari for their invaluable support and the privilege of working alongside them. Their talent, dedication, and camaraderie have been a constant source of inspiration, shaping both my academic and professional growth. The insightful discussions and shared experiences have made this journey not only rewarding but profoundly formative.

A special thank you to Davide Palma, Sara Pederzoli, Sara Ferrari, Diego Mercoliano, Emiliano Maccaferri, Giacomo Salici, Angelo Mozzillo, Paolo Attardi, Michele Giarletta, Vincenzo Lapadula, Felicia Puzone, Riccardo Santi, Vincenzo Macellaro, Andrea Agguzzoli, Marco Savarese, Carmenia Basile, Francesca Palazzo, Giovanni Malaguti, Biagio Grimolizzi, Stefano Politanó, Marco Pirrelli, Antonio Solida, Elisa Tomisani, Luca Catalano, Valeria Coloca, Manuel Valbusa, Carmine Zaccagnino, Michele Mosca, Giuseppe Orefice, Aslam Kalam, Marco Francesco Sette, Felice Schena, Adeel Aslam, Luca Corrado, Antonio De Blasi, and Gianmarco Lusvardi. Whether our paths have already diverged or will in time, I will always cherish the moments we shared. Every challenge, lesson, and connection has contributed to my growth, and I am grateful for each one.

No matter where life takes you, know that you have my sincere support in all your endeavors. I wish you happiness and success in every pursuit. Though our journeys may lead us in different directions, my appreciation remains steadfast, and perhaps one day, our paths will cross again in unexpected and meaningful ways.

With heartfelt gratitude and best wishes for the future, I thank you all.
